---
title: "Group 6 - Project"
author: "Group 6 team members"
date: "October 9, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
library(ggplot2)
Meddata <- read.csv("Medicare_Provider_Charge_Inpatient_DRGALL_FY2014.csv")

```

## 1. Abstract or Executive Summary
summarise our findings here.



## 2. Introduction
Type the introduction here
- what dataset are we studying?
- what type of data
- what year
- source? 


## 2.1 Description of the dataset

```{r, echo = FALSE}
NoObsx <- nrow(Meddata) #number of observations
NoVarx <- ncol(Meddata) #number of variables
NoDRG <- length(levels(Meddata$DRG.Definition)) #number of categories in DRG definitions

print(paste0("There are ", format(NoObsx, big.mark = ","), " rows of data across ", NoVarx, " columns of variables. Notably, there were ", NoDRG, " types of clinical conditions and procedures furnished by the hospitals during patients' stay."))
```

The type of clinical conditions and procedures were specific. For example,

```{r, echo = FALSE}
head(levels(Meddata$DRG.Definition))
```


The descriptions of the variables are summarised in the next section.



## 2.2 Definitions of Variables

The definitions of the variables are taken from the file provided in the source (Link: https://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Medicare-Provider-Charge-Data/Inpatient2014.html), "Medicare Inpatient PUF Methodology [PDF, 185KB]".

|Variable| Description|
|-----------------------|--------------------------------------------------------------------------------------|
|DRG Definition| The code and description identifying the MS-DRG. MS-DRGs are a classification system that groups similar clinical conditions (diagnoses) and the procedures furnished by the hospital during the stay|
|Provider Id| The CMS Certification Number (CCN) assigned to the Medicare certified hospital facility|
|Provider Name| The name of the provider|
|Provider Street Address| The provider’s street address|
|Provider City| The city where the provider is located|
|Provider State| The two-letter code of the state where the provider is located|
|Provider Zip Code| The provider’s zip code|
|Hospital Referral Region (HRR) Description| The Hospital Referral Region (HRR) where the provider is located|
|Total Discharges| The number of discharges billed by the provider for inpatient hospital services|
|Average Covered Charges| The provider's average charge for services covered by Medicare for all discharges in the MS-DRG. These will vary from hospital to hospital because of differences in hospital charge structures|
|Average Total Payments|The average total payments to all providers for the MS-DRG including the MSDRG amount, teaching, disproportionate share, capital, and outlier payments for all cases. Also included for in average total payments are co-payment and deductible amounts that the patient is responsible for and any additional payments by third parties for coordination of benefits|
|Average Medicare Payments|The average amount that Medicare pays to the provider for Medicare's share of the MS-DRG. Average Medicare payment amounts include the MS-DRG amount, teaching, disproportionate share, capital, and outlier payments for all cases. Medicare payments DO NOT include beneficiary co-payments and deductible amounts nor any additional payments from third parties for coordination of benefits. Note: In general, Medicare FFS claims with dates-of-service or dates-of-discharge on or after April 1, 2013, incurred a 2 percent reduction in Medicare payment. This is in response to mandatory across-the-board reductions in Federal spending, also known as sequestration.| 



## 3 Descriptive Statistics 
- univariate stats
totaldischarges <- sum(Meddatax$Total.Discharges) #Total number of discharges covered by medicare in 2015
totalpayments <- sum(Meddatax$TotalPayments) #Total payments made to hospitals by Medicare in 2015
avepmtperdisc <- totalpayments / totaldischarges

print(paste0("The total number of discharges covered by medicare in FY 2014 was ", format(totaldischarges, big.mark = ","), "."))
[1] "The total number of discharges covered by medicare in FY 2014 was 7,297,885."

print(paste0("The total number of payments made by medicare to the providers in FY 2014 was $", format(totalpayments, nsmall = 2, big.mark = ","), "."))
[1] "The total number of payments made by medicare to the providers in FY 2014 was $90,834,586,996.93."

print(paste0("The average payment made per discharge in FY 2014 was $", format(avepmtperdisc, nsmall =2, big.mark = ","), "."))
"The average payment made per discharge in FY 2014 was $12,446.70."


- bivariate stats
- some plots of the stats
- some written interpretation of the stats and plots



## 4 Correlation Analyses
- correlation analyses
- covered charge vs total payments?
- covered charge vs total payments by state / by DRG?
- others
- written interpretation of the correlation tests. scatter plots?


## 5 Regression Analyses
- regression analyses
- what is our dependent variable? what are we trying to find out?
- independent variables and justifications?
- stargazer if we have more than 1 model



## 6 Results and Discussion
- more in-depth discussion of our findings?
- any conclusion?



## 7 References
- any references used? acknowledgement to dataset and definitions of variables


