---
title: "Group 6 - Project"
author: "Group 6 team members"
date: "October 9, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Definitions of Variables

The definitions of the variables are taken from the file provided in the source (Link: https://www.cms.gov/Research-Statistics-Data-and-Systems/Statistics-Trends-and-Reports/Medicare-Provider-Charge-Data/Inpatient2014.html), "Medicare Inpatient PUF Methodology [PDF, 185KB]".

|Variable| Description|
|-----------------------|--------------------------------------------------------------------------------------|
|DRG Definition| The code and description identifying the MS-DRG. MS-DRGs are a classification system that groups similar clinical conditions (diagnoses) and the procedures furnished by the hospital during the stay|
|Provider Id| The CMS Certification Number (CCN) assigned to the Medicare certified hospital facility|
|Provider Name| The name of the provider|
|Provider Street Address| The provider’s street address|
|Provider City| The city where the provider is located|
|Provider State| The two-letter code of the state where the provider is located|
|Provider Zip Code| The provider’s zip code|
|Hospital Referral Region (HRR) Description| The Hospital Referral Region (HRR) where the provider is located|
|Total Discharges| The number of discharges billed by the provider for inpatient hospital services|
|Average Covered Charges| The provider's average charge for services covered by Medicare for all discharges in the MS-DRG. These will vary from hospital to hospital because of differences in hospital charge structures|
|Average Total Payments|The average total payments to all providers for the MS-DRG including the MSDRG amount, teaching, disproportionate share, capital, and outlier payments for all cases. Also included for in average total payments are co-payment and deductible amounts that the patient is responsible for and any additional payments by third parties for coordination of benefits|
|Average Medicare Payments|The average amount that Medicare pays to the provider for Medicare's share of the MS-DRG. Average Medicare payment amounts include the MS-DRG amount, teaching, disproportionate share, capital, and outlier payments for all cases. Medicare payments DO NOT include beneficiary co-payments and deductible amounts nor any additional payments from third parties for coordination of benefits. Note: In general, Medicare FFS claims with dates-of-service or dates-of-discharge on or after April 1, 2013, incurred a 2 percent reduction in Medicare payment. This is in response to mandatory across-the-board reductions in Federal spending, also known as sequestration.| 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
